bounding_box_preprocesing

### 2021-05-04 preprocessing/step0_get_human_annotations/face_hands/analysis/preprocess_turk_detections.Rmd
restructure preprocessing folder

```{r setup, echo = FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(lmerTest)
library(viridis)
library(magick)
library(egg)
theme_set(theme_few())
```

# Preprocessing
## Not finished cleaning this up yet...
```{r}
jf <- paste0(here::here(), '/data/turk_data/raw/face_hand_detections/Batch_3858789_batch_results.csv')

@@

summary <- jd %>%
  group_by(WorkerId) %>%
  summarize(count_images = n(), avg_time = mean(WorkTimeInSeconds))

jd$response = jd$`Answer.trial-1.label`
agreement <- jd %>%
  group_by(Input.img_src1) %>%
  summarize(agree = response[1] == response[2])
```

@@

## Would like to get rando responses in .label field here:

### Sometimes we get NAs and they end up in ".label fields", but not every trial has them (so it throws errors in a loop). I'm too tired to write an appropriate function so just leaving those NAs for now but the data is there. Starter code is below.

# empty_labels = as.character(array(matrix(data=NA, nrow=1, ncol=num_workers)))
# 
# 
# for (trial_ind in trial_indexes){
#   field_to_check = paste0("jd$`Answer.trial-",trial_ind,".label`")
#   if (!field_to_check %in% colnames(jd)){
#     jd$(field_to_check) = empty_labels
#   }
# }

@@

### Write out csv for use in analysis
```{r}
write_csv(d.filtered,'turk_annotations_dec5.csv')
```

>>>>

```{r setup, echo = FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(lmerTest)
library(viridis)
library(magick)
library(here)
library(lubridate)
library(egg)
theme_set(theme_few())
```

# Preprocessing
```{r}
jf <- paste0(here::here(), '/data/turk_data/raw/face_hand_detections/Batch_3858789_batch_results.csv')

@@

summary <- jd %>%
  group_by(WorkerId) %>%
  summarize(avg_time = mean(WorkTimeInSeconds))

```

@@

## Would like to get rando responses in .label field here:
### Sometimes we get NAs and they end up in ".label fields", but not every trial has them (so it throws errors in a loop). I'm too tired to write an appropriate function so just leaving those NAs for now but the data is there. Starter code is below.
# empty_labels = as.character(array(matrix(data=NA, nrow=1, ncol=num_workers)))
# 
# 
# for (trial_ind in trial_indexes){
#   field_to_check = paste0("jd$`Answer.trial-",trial_ind,".label`")
#   if (!field_to_check %in% colnames(jd)){
#     jd$(field_to_check) = empty_labels
#   }
# }

@@

### Write out csv for use in analysis
```{r}
write_csv(d.filtered,paste0(here::here, '/data/turk_data/face_hand_detections', today(), '.csv'))
```

### 2021-05-04 preprocessing/step4_create_bounding_box_summaries.Rmd
restructure preprocessing folder

## Paths to raw outputs & datafiles
```{r}
op_file_dir = here::here("data/op_outputs_per_vid_full_set/")
op_files = dir(op_file_dir)
# op_files = op_files [1] # for testing

@@

## Main detections: read in bounding box outputs from each vid, summarize and compile.
```{r}
reload_data=TRUE
# instead of loading each vid, load summary...
# load(here::here('data/preprocessed_data/all_vid_data_from_bbs_may2020.RData'))

@@

if (reload_data){
vid_index = 0
for (vid_file in op_files) {
  vid_index = vid_index + 1
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid_full_set/', vid_file)
   this_vid_data <- readRDS(vid_file_path)

@@

   this_vid <- this_vid_data %>%
      filter(!is.na(height)) %>%
      mutate(area = height * width) %>%
      filter(mean_confidence >.1 ) %>%
      group_by(label, child_id, vid_name) %>%
      summarize(num_detect = length(height), avg_area = median(area), avg_height = median(height), avg_width = median(width), avg_left = median(left), avg_top = median(top))

@@

save(all_vid_bbs,file=here::here('data/preprocessed_data_2021/bounding_box_summaries.RData'))

>>>>

## Paths to raw outputs & datafiles
```{r}
op_file_dir = here::here("data/op_outputs_per_vid_rds/")
op_files = dir(op_file_dir)
# op_files = op_files [1] # for testing

@@

## Main detections: read in bounding box outputs from each vid, summarize and compile.
```{r}
reload_data=TRUE
# instead of loading each vid, load summary...

@@

if (reload_data){
vid_index = 0
for (vid_file in op_files) {
  vid_index = vid_index + 1
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid_rds/', vid_file)
   this_vid_data <- readRDS(vid_file_path)

@@

   this_vid <- this_vid_data %>%
      filter(!is.na(height)) %>%
      filter(mean_confidence > 0) %>% # sanity
      mutate(area = height * width) %>%
      group_by(label, child_id, vid_name) %>%
      summarize(num_detect = length(height), avg_area = median(area), avg_height = median(height), avg_width = median(width), avg_left = median(left), avg_top = median(top))

@@

save(all_vid_bbs,file=here::here('data/preprocessed_data_2021/bounding_box_summaries_all.RData'))
